\documentclass[a4paper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,margin=1.25cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{lmodern}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{5pt}

\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=2pt,
  topsep=2pt,
  parsep=0pt,
  partopsep=0pt
}

\newcommand{\resumeSubheading}[4]{
  \textbf{#1} \hfill #2 \\
  \textit{#3} \hfill #4 \\
}

\begin{document}

\begin{center}
  {\LARGE\textbf{Bartosz Litwa}} \\
  \vspace{3pt}
  Software Engineer \textbar{} Full Stack .NET Developer + DevOps \\
  \vspace{3pt}
  Warsaw, Poland \textbar{} +48 530 534 774 \textbar{}
  \href{mailto:bartosz.maciej.litwa@gmail.com}{bartosz.maciej.litwa@gmail.com} \\
  \href{https://litwa.dev}{litwa.dev} \textbar{}
  \href{https://github.com/BartoszLitwa}{github.com/BartoszLitwa}
  \textbar{}
  \href{https://www.linkedin.com/in/bartoszlitwa/}{linkedin.com/in/bartoszlitwa}
\end{center}

\vspace{-8pt}

\section*{Summary}

Full-stack .NET developer with 4+ years of experience building
microservices-based and multitenant applications using .NET, Angular,
Azure, and Azure DevOps. Strong focus on cloud architecture, CI/CD,
data migration, cost optimization, automated testing, and developer
experience.

\vspace{-4pt}

\section*{Experience}

\resumeSubheading
  {KPMG Poland}
  {Nov 2022 -- Present}
  {Junior .NET Developer II -> .NET Developer III -> Senior Test Automation}
  {Warsaw, Poland}
  \vspace{-10pt}

\begin{itemize}
  \item Built and maintained applications using .NET, Angular, Azure, and
        Azure DevOps, including CI/CD processes.
  \item Contributed to the migration of a microservice from Azure Cosmos DB
        to Azure SQL with Entity Framework Core, including data migrations
        and cleanup.
  \item Introduced Cosmos DB container bundling in a multitenant
        application, reducing cost by 90\% and improving RU management.
  \item Set up supporting Azure Data Factory infrastructure, integrating
        Azure Functions, Managed Identities, Key Vault, RBAC, Cosmos DB,
        Azure SQL, and Azure Blob Storage.
  \item Supported runtime tenant sharding across Azure SQL, Cosmos DB, and
        Blob Storage for multiple microservices.
  \item Built import, export, and migration flows for dynamic
        configurations powering data-driven forms, with in-memory
        optimizations for better performance.
  \item Maintained Selenium automation tests in C\# and supported migration
        to Playwright with TypeScript to improve stability and test
        coverage.
  \item Implemented .NET Aspire with Podman to orchestrate the local
        development environment and improve developer experience.
\end{itemize}

\vspace{4pt}

\resumeSubheading
  {Coded Projects}
  {Apr 2022 -- Jul 2022}
  {Junior Full Stack Developer}
  {Warsaw, Poland}
  \vspace{-10pt}

\begin{itemize}
  \item Developed full-stack features using React, TypeScript, Chart.js,
        C\#, ASP.NET Core, SQL, Entity Framework, and stored procedures in
        a microservices-based environment.
  \item Contributed to code reviews, debugging, testing, and UI
        improvements across frontend and backend applications.
\end{itemize}

\vspace{4pt}

\resumeSubheading
  {Polish Rope Pulling Association}
  {Feb 2021 -- May 2021}
  {Junior Software Engineer}
  {Warsaw, Poland}
\vspace{-10pt}

\begin{itemize}
  \item Built a C\# integration tool to sort and merge local files for
        migration to a web service.
  \item Automated repetitive workflows with Excel VBA, reducing manual
        errors and making data migration 10x faster.
\end{itemize}

\section*{Certifications}

\begin{itemize}
  \item Microsoft Certified: Azure Developer Associate AZ-204, Azure AI Fundamentals AI-900, Azure Data Fundamentals DP-900, Azure Fundamentals AZ-900
\end{itemize}

\vspace{-4pt}

\section*{Project}

\resumeSubheading
  {RentifyNow (\href{https://rentifynow.com}{rentifynow.com})}
  {Ongoing}
  {Founder / Developer}
  {Personal SaaS Project}
  \vspace{-10pt}

\begin{itemize}
  \item Building a self-hosted platform for solo landlords to manage properties,
        tenants, finances, documents, messages with built in AI assistant using .NET and Angular.
  \item Own the VPS infrastructure end-to-end, including deployment,
        environment configuration, and ongoing operations.
\end{itemize}

\vspace{-4pt}

\section*{Education}

\resumeSubheading
  {Polish-Japanese Academy of Information Technology}
  {Oct 2021 -- Jul 2025}
  {Bachelor of Engineering in Computer Science}
  {Warsaw, Poland}
  \vspace{-10pt}

\vspace{-4pt}

\section*{Skills}

\textbf{Languages:} C\#, TypeScript, JavaScript, SQL, HTML, CSS \\
\textbf{Frameworks:} .NET, ASP.NET Core, Angular, React, Entity Framework
Core \\
\textbf{Cloud \& DevOps:} Azure, Azure DevOps, YAML Pipelines, CI/CD,
Azure Functions, Azure App Service, Azure Storage, Azure Cosmos DB,
Azure SQL, Azure Data Factory, Key Vault, Managed Identities, RBAC \\
\textbf{Testing \& Tools:} Playwright, Selenium, Git, Postman, Bruno, Docker, Podman, .NET Aspire \\
\textbf{Languages Spoken:} Polish (Native), English (C1), Spanish (Basic)

\end{document}